---
title: "analyze_recog_dataframe"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
library(brms)
#library(Rmisc)
library(tidyboot)
```

# Recognition timecourse analyses 

#### load in data
```{r}
version = 'cogsci' # '2.0, i.e. no interrupting & balanced contexts'
path = ifelse(version == 'cogsci', 'run3run4.csv', 'run5_submitButton.csv')

d.recog <- read_csv('../../results/csv/graphical_conventions_recog_data_bis.csv') %>%
  mutate(version = factor(version, levels = c("refgame","yoked","scrambled40"), labels = c("communication", "yoked", "shuffled" ))) 
```

## Analysis of task performance efficiency (BIS, balancing accuracy vs. drawDuration)

### get bootstrapped relative BIS x repetition, broken out by version
```{r}
d.recog.boot = d.recog %>%
  group_by(version,repetition_1) %>%
  tidyboot_mean(col=bis_relative) %>%
  ungroup()
```
### plotting BIS  from refgame, yoked, and scrambled40 experiments
```{r}
d.recog.boot %>%  
  ggplot(aes(x = repetition_1, y = empirical_stat, color = version, fill = version)) +
  geom_line(size=1.5) +
  # geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper, width = 0)) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.2, color = NA) +
  theme_few() +
  ylab('relative efficiency') +
  xlab('repetition') +
  # geom_hline(aes(yintercept=0.25),linetype='dashed') +
  scale_x_continuous(breaks=seq(1,8,by=1)) + 
  scale_color_manual(values=c("#163c4e", "#658da0", '#54792f')) + 
  scale_fill_manual(values=c("#163c4e", "#658da0", '#54792f')) +   
  theme(legend.position = c(0.18, 0.8), text = element_text(size=18), element_line(size=1), element_rect(size=2, color="#00000")) +
  theme(legend.text=element_text(size=12), legend.background = element_rect(fill="transparent"))
ggsave('../../results/plots/recog_BIS_timeseries.pdf', width=14, height = 10, units='cm')
```


### mixed-effects modeling of BIS (balancing accuracy vs. drawDuration) from communication vs. yoked experiments

```{r}
m1 <- summary(lmer(bis_relative ~ version * repetition + (1 + version * repetition | orig_gameID), 
              data = d.recog %>% filter(version %in% c('communication', 'yoked'))))
summary(m1)

```

### mixed-effects modeling of BIS (balancing accuracy vs. drawDuration) from yoked vs. scrambled40 experiments
```{r}
m2<-summary(lmer(bis_relative ~ version * repetition + (1 + repetition | gameID), 
              data = d.recog %>% filter(version %in% c('yoked', 'shuffled'))))
summary(m2)
```


## Analysis of change in raw accuracy & RT across all three groups: communication, yoked, shuffled
```{r}
d.acc <- read_csv(paste0('../../results/csv/graphical_conventions_recog_data', path)) %>%
  mutate(version = factor(version, levels = c("refgame","yoked","scrambled40"), labels = c("communication", "yoked", "shuffled" ))) %>%
  filter(condition == 'repeated') %>%
  group_by(version,gameID,repetition) %>%
  summarize(accuracy=mean(correct), RT = mean(logRT))

d.acc %>%
  gather(measure, value, accuracy, RT) %>%
  filter(repetition %in% c(0,7)) %>%
  group_by(measure, repetition, version) %>%
  summarize(m=mean(value)) %>%
  spread(repetition, m) %>%
  mutate(diff = `7` - `0`) 
```

#### Comparing communication and yoked accuracies

```{r}

d.acc <- read_csv('../../results/graphical_conventions_recog_data.csv') %>%
  mutate(version = factor(version, levels = c("refgame","yoked","scrambled40"), labels = c("communication", "yoked", "shuffled" ))) %>%
  filter(version %in% c('communication','yoked')) %>%
  group_by(version,gameID,repetition) %>%
  summarize(accuracy=mean(correct))

m1a <- summary(lmer(accuracy ~ version + (1 | gameID),
              data = d.acc))
summary(m1a)
```
##### Plotting accuracy timecourse for communication and yoked
```{r}
d.acc.boot = d.acc %>%
  group_by(version,repetition) %>%
  tidyboot_mean(col=accuracy) %>%
  ungroup()

d.acc.boot %>%  
  ggplot(aes(x = repetition, y = empirical_stat, color = version, fill = version)) +
  geom_line(size=1.5) +
  # geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper, width = 0)) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.2, color = NA) +
  theme_few() +
  ylab('accuracy') +
  xlab('repetition') +
  geom_hline(aes(yintercept=0.25),linetype='dashed') +
  scale_x_continuous(breaks=seq(1,8,by=1)) + 
  scale_color_manual(values=c("#163c4e", "#d07e93", '#54792f')) + 
  scale_fill_manual(values=c("#163c4e", "#d07e93", '#54792f')) +   
  theme(legend.position = c(0.18, 0.8), text = element_text(size=18), element_line(size=1), element_rect(size=2, color="#00000")) +
  theme(legend.text=element_text(size=12), legend.background = element_rect(fill="transparent"))
```



#### comparing yoked and shuffled accuracies

```{r}

d.acc <- read_csv('../../results/graphical_conventions_recog_data.csv') %>%
  mutate(version = factor(version, levels = c("refgame","yoked","scrambled40"), labels = c("communication", "yoked", "shuffled" ))) %>%
  filter(version %in% c('yoked','shuffled')) %>%
  group_by(version,gameID,repetition) %>%
  summarize(accuracy=mean(correct))

m1b <- summary(lmer(accuracy ~ version + (1 | gameID),
              data = d.acc))
summary(m1b)

```

#### Plotting accuracy timecourse for yoked and shuffled
```{r}
d.acc.boot = d.acc %>%
  group_by(version,repetition) %>%
  tidyboot_mean(col=accuracy) %>%
  ungroup()

d.acc.boot %>%  
  ggplot(aes(x = repetition, y = empirical_stat, color = version, fill = version)) +
  geom_line(size=1.5) +
  # geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper, width = 0)) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.2, color = NA) +
  theme_few() +
  ylab('accuracy') +
  xlab('repetition') +
  geom_hline(aes(yintercept=0.25),linetype='dashed') +
  scale_x_continuous(breaks=seq(1,8,by=1)) + 
  scale_color_manual(values=c("#163c4e", "#d07e93", '#54792f')) + 
  scale_fill_manual(values=c("#163c4e", "#d07e93", '#54792f')) +   
  theme(legend.position = c(0.18, 0.8), text = element_text(size=18), element_line(size=1), element_rect(size=2, color="#00000")) +
  theme(legend.text=element_text(size=12), legend.background = element_rect(fill="transparent"))
```
