---
title: "analyze_refgame_dataframe"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
library(brms)
#library(Rmisc)
library(tidyboot)
```

## Import group data

```{r}
d <- read_csv('../../results/graphical_conventions.csv')  %>% select(-png)
d.bis.drawDuration <- read_csv('../../results/graphical_conventions_bis_score_drawDuration.csv')  %>% select(-X1)
d.bis.numStrokes <- read_csv('../../results/graphical_conventions_bis_score_numStrokes.csv') %>% select(-X1)
```

Some statistics we report

```{r}
d %>% group_by(generalization) %>% summarize(l = length(unique(gameID)))
```

```{r}
d.bis.drawDuration
```

## Generate histograms for numCurvesPerSketch and numStrokes 

```{r}
d %>% 
  group_by(numCurvesPerSketch) %>% ggplot(aes(x = numCurvesPerSketch)) + geom_histogram()
```

```{r}
d %>% 
  group_by(numStrokes) %>% ggplot(aes(x = numStrokes)) + geom_histogram()
```

## Behavioral Results: BIS analysis (on drawDuration)

```{r}
# generate "baseline" bis dataframe that computes pre-phase BIS, grouped by condition and gameID
bbis <-d.bis.drawDuration %>%
      filter(repetition==0) %>%
      group_by(condition,gameID) %>%
      summarize(bis_score = mean(bis_score))

# add this "baseline" bis to each row of original bis dataframe
d.bis.drawDuration <- inner_join(d.bis.drawDuration, bbis, by = c('condition','gameID'), suffix = c("","_baseline")) %>%
                      mutate(bis_score_relative = bis_score - bis_score_baseline) %>%
                      mutate(repetition_1 = repetition + 1)
```

```{r}
d.bootstrap <- d.bis.drawDuration %>% group_by(condition, repetition_1) %>% tidyboot_mean(column=bis_score_relative)

d.bootstrap %>%
  ggplot(aes(x=repetition_1,y=empirical_stat, color=condition, fill=condition)) + 
    geom_ribbon(aes(ymin=ci_lower, ymax = ci_upper), alpha =.25, color=NA,
                data = d.bootstrap %>% filter(condition == 'repeated')) + # position = dodge, 
    geom_line(size=1.5)+#data = d.bootstrap %>% filter(condition == 'repeated')) + 
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                  data = d.bootstrap %>% filter(condition == 'control')) + 
    # geom_point(size = 5) + 
    ylab("relative efficiency") +
    xlab("repetition") +
    theme_few() +
    scale_x_continuous(breaks = round(seq(min(d.bootstrap$repetition_1), max(d.bootstrap$repetition_1), by =1),1)) + 
    scale_y_continuous(breaks = seq(-0.5,2.5,0.5)) +
    scale_color_manual(values=c("#808080", "#163c4e")) + 
    scale_fill_manual(values=c("#808080", "#163c4e")) + 
    theme(legend.position = c(0.8, 0.2), text = element_text(size=18), element_line(size=1), element_rect(size=2, color="#00000"))
ggsave('../../results/plots/refgame_BIS_timeseries.pdf', width=14, height = 10, units='cm')

```


## Mixed-effects model for BIS (on drawDuration by phase)

```{r}
# preferred model definition for interaction between repetition and condition for bis -- has right syntax but doesn't converge
# interaction_lmm <- lmer(bis_score ~ phase * condition + (1 + phase*condition | target) + (1 + phase*condition | gameID)

input <- d.bis.drawDuration %>%
         filter(repetition == 0 | repetition == 7) %>% 
         mutate(phase = as.factor(ifelse(repetition == 0, 'pre', 'post')),
                condition = as.factor(condition))

contrasts(input$phase) <- c(-.5, .5)
contrasts(input$condition) <- c(-.5, .5)

# alternative model definition (removing target-wise random effects for phase*condition interaction)
interaction_lmm <- lmer(bis_score ~ phase * condition + (1 + phase*condition | gameID), 
                        data = input)

print(summary(interaction_lmm))
```


## accuracy differences between condition in pre phase 

```{r}
d %>%
   mutate(phase = as.factor(ifelse(repetition == 0, 'pre', 'post')),
          condition = as.factor(condition)) %>%
   filter(phase == 'pre') %>%
   mutate(binaryOutcome = ifelse(outcome == 'True', 1, 0)) %>%
   group_by(gameID, condition) %>%
  summarize(acc = mean(binaryOutcome)) %>%
  spread(condition, acc) %>%
  mutate(diff = repeated - control) %>%
  ungroup() %>%
  tidyboot_mean(diff)
```


## Mixed-effects model for BIS (on numStrokes by phase)

```{r}
input <- d.bis.numStrokes %>%
         filter(repetition == 0 | repetition == 7) %>% 
         mutate(phase = as.factor(ifelse(repetition == 0, 'pre', 'post')),
                condition = as.factor(condition))

contrasts(input$phase) <- c(-.5, .5)
contrasts(input$condition) <- c(-.5, .5)

# alternative model definition (removing game-wise random effects for phase*condition interaction)
interaction_lmm <- lmer(numStrokes ~ phase * condition + (1 + phase*condition | target), 
                        data = input)

print(coef(summary(interaction_lmm)))
```

## Mixed-effects model on accuracy (instead of just BIS)

```{r}

input <- d %>%
         filter(repetition == 0 | repetition == 7) %>% 
         mutate(phase = as.factor(ifelse(repetition == 0, 'pre', 'post')),
                condition = as.factor(condition),
                outcome = as.factor(outcome))

# alternative model definition (removing game-wise random effects for phase*condition interaction)
interaction_lmm <- glm(outcome ~ phase * condition , family='binomial',
                        data = input)

summary(interaction_lmm)
```

## Raw accuracy in pre and post

```{r}
d %>% 
  filter(phase== 'pre'| phase == 'post') %>%
  mutate(outcome_binary = ifelse(outcome == 'True', 1, 0)) %>%
  group_by(phase,condition) %>%
  tidyboot_mean(column=mean(outcome_binary))

```

## compute subject-wise, condition-wise change in accuracy from pre to post
```{r}

d_acc <- d %>%
  filter(phase== 'pre'| phase == 'post') %>%
  mutate(outcome_binary = ifelse(outcome == 'True', 1, 0)) %>%
  group_by(gameID,phase,condition) %>%
  summarize(accuracy=mean(outcome_binary)) %>%
  spread(phase, accuracy) %>%
  mutate(diff = post - pre) %>%
  group_by(condition) %>%
  tidyboot_mean(column=mean(diff)) 

d_acc

d_acc %>%
    ggplot(aes(x = condition, y =empirical_stat)) +
    geom_bar(stat = 'identity') +
    geom_errorbar(aes(ymax = ci_upper, ymin = ci_lower), width = 0) +
    theme_few() +
    ylim(-.25, .25)
  
```

## fit lmer model to subject-wise, condition-wise change in num strokes from pre to post
```{r}

m_strokes <- lmer(numStrokes ~ repetition + (1 + repetition | gameID) + (1 | target), data = d %>% filter(condition=='repeated'))
summary(m_strokes)

d %>%
  filter(condition == 'repeated') %>%
  mutate(repetition = repetition + 1) %>%
  group_by(repetition) %>%
  tidyboot_mean(numStrokes) %>%
  ggplot(aes(x = repetition, y = empirical_stat)) +
    geom_point() +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F, color = 'black') +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    theme_few() +
    scale_x_continuous(labels = c(1,2,3,4,5,6,7,8), breaks = c(1,2,3,4,5,6,7,8)) +
    ylab('number of strokes') +
    ylim(1,8) +
    theme(legend.position = c(0.5, 0.8), text = element_text(size=18), 
          element_line(size=1), element_rect(size=2, color="#00000")) +
  
ggsave('../../../graphical_conventions_latex/cogsci19/figures/source/num_strokes.pdf', height = 10, width = 7, units = 'cm', useDingbats = F)


```


# Similarity-based analyses

Import pre-processed matrices from ipynb

```{r}
source('./helpers.R')
library(broom)
detach('package:lmerTest')
M_mat = read_csv('../../data/sketch_features/no_crop/METADATA_sketch.csv') %>%
  filter(condition == 'repeated') %>%
  select(gameID, target, repetition, trial_num, feature_ind) %>%
  mutate(feature_ind = feature_ind + 1,
         trial_num = as.numeric(trial_num),
         repetition = as.numeric(repetition)) %>% # Have to correct for R 1-indexing...
  arrange(gameID, target, repetition) 
F_mat_raw_nonorm = as.matrix(read_delim('../../data/sketch_features/no_crop/FEATURES_FC6_sketch_no-channel-norm.txt', 
                                   delim=',', col_names=F))

colnames(F_mat_raw_nonorm) <- NULL
```

## Within-interaction drift

```{r}
true_lmer.drift <- make_within_df(M_mat, F_mat_raw_nonorm, 'cor') %>% filter(rep1 == 0) %>% ungroup()
true_lmer.drift.out <- lmer(sim ~ poly(rep2,2) + (1  | gameID) + (1 | target), data = true_lmer.drift)

permuted_tstats.drift <- map_dbl(seq_len(1000), ~ M_mat %>%
 # scrambles repetition
  group_by(target, repetition) %>% mutate(gameID = sample(gameID)) %>% ungroup() %>%
  arrange(gameID, target, repetition) %>%
  make_within_df(F_mat_raw_nonorm, 'cor') %>%
  filter(rep1 == 0) %>% 
  # turns into a list to make `map` happy
  ungroup() %>%  mutate(sample_id = 1) %>% split(.$sample_id) %>%
  map(~ lmer(sim ~ poly(rep2,2) + (1 | gameID) + (1 | target), data = .)) %>%
  map(~ (tidy(., effects = 'fixed') %>% filter(term == 'poly(rep2, 2)1'))$statistic) %>%
  unlist())

cat('CI for drift analysis=', sort(permuted_tstats.drift)[25], sort(permuted_tstats.drift)[975])
cat('true for drift analysis=', (tidy(true_lmer.drift.out, effects = 'fixed') %>% filter(term == 'poly(rep2, 2)1'))$statistic)
```

```{r}
num_permutations <- 1000
empirical.drift <- compute_within_drift(M_mat, F_mat_raw_nonorm, 'empirical', method = 'cor', nboot = 1000)
baselines.drift <- map_dfr(seq_len(num_permutations), ~M_mat %>%
  group_by(target, repetition) %>%
  mutate(gameID = sample(gameID)) %>% # shuffle within target-rep 
  ungroup() %>%
  arrange(gameID, target, repetition) %>%
  compute_within_drift(F_mat_raw_nonorm, .x, method = 'cor')) # this passes in the iteration number
```

```{r}
d.toplot.drift <- baselines.drift %>%
  group_by(`rep diff`) %>%
  summarize(`ci_upper`=quantile(empirical_stat, probs=0.975),
            `ci_lower`=quantile(empirical_stat, probs=0.025),
            `empirical_stat`=quantile(empirical_stat, probs=0.5)) %>%
  mutate(sample_id = 'baseline') %>%
  rbind(empirical.drift %>% select(-n, -mean)) 

ggplot(d.toplot.drift, aes(x = `rep diff`, y = empirical_stat, 
             fill = sample_id, color = sample_id, group = sample_id)) +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.5, color = NA,
                d.toplot.drift %>% filter(sample_id == 'baseline')) +
    #geom_line(alpha = 0, size = 2) +
    geom_line(size = 1, linetype = 'dashed', data = d.toplot.drift %>% filter(sample_id == 'baseline')) +
    geom_point(size = 2, data = d.toplot.drift %>% filter(sample_id == 'empirical')) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0,
                  data = d.toplot.drift %>% filter(sample_id == 'empirical')) +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F,
                data = d.toplot.drift %>% filter(sample_id == 'empirical')) +
    scale_color_manual(values=c("#d07e93", "#163c4e")) + 
    scale_fill_manual(values=c("#d07e93", "#163c4e")) + 
    scale_x_discrete(labels = c('(1,2)','(1,3)', '(1,4)', '(1,5)', '(1,6)' ,'(1,7)','(1,8)')) +
    ylim(.5, .8) +
    ylab('correlation') +
    ggtitle('drift from initial') +
    theme_few() +
    xlab('repetition pair') +
    guides(color = F, fill = F) +
    theme(legend.position = c(0.5, 0.8), text = element_text(size=18), 
          element_line(size=1), element_rect(size=2, color="#00000"))

ggsave('../../../graphical_conventions_latex/cogsci19/figures/source/drift.pdf', height = 10, width = 7, units = 'cm', useDingbats = F)
```

## Within-interaction convergence

```{r}
true_lmer.within <- make_within_df(M_mat, F_mat_raw_nonorm, 'cor') %>% filter(rep2 == rep1 + 1) %>% ungroup()
summary(lmer(sim ~ poly(rep1,2) + (1  | gameID) + (1 | target), data = true_lmer.within))

permuted_tstats.within <- map_dbl(seq_len(1000), ~ M_mat %>%
 # scrambles repetition
  group_by(target, repetition) %>% mutate(gameID = sample(gameID)) %>% ungroup() %>%
  arrange(gameID, target, repetition) %>%
  make_within_df(F_mat_raw_nonorm, 'cor') %>%
  filter(rep2 == rep1 + 1) %>% 
  # turns into a list to make `map` happy
  ungroup() %>%  mutate(sample_id = 1) %>% split(.$sample_id) %>%
  map(~ lmer(sim ~ poly(rep1,2) + (1 | gameID) + (1 | target), data = .)) %>%
  map(~ (tidy(., effects = 'fixed') %>% filter(term == 'poly(rep1, 2)1'))$statistic) %>%
  unlist())

cat('CI for within analysis=', sort(permuted_tstats.within)[25], sort(permuted_tstats.within)[975])
```

compute both true empirical & permuted output

```{r}
num_permutations <- 1000
empirical.within <- compute_within_convergence(M_mat, F_mat_raw_nonorm, 'empirical', method = 'cor', nboot = 1000)
baselines.within <- map_dfr(seq_len(num_permutations), ~M_mat %>%
  group_by(target, repetition) %>%
  mutate(gameID = sample(gameID)) %>% # shuffle within target-rep 
  ungroup() %>%
  arrange(gameID, target, repetition) %>%
  compute_within_convergence(F_mat_raw_nonorm, .x, method = 'cor')) # this passes in the iteration number
```

Plot with permutations

```{r}
d.toplot <- baselines.within %>%
  group_by(`rep diff`) %>%
  summarize(`ci_upper`=quantile(empirical_stat, probs=0.975),
            `ci_lower`=quantile(empirical_stat, probs=0.025),
            `empirical_stat`=quantile(empirical_stat, probs=0.5)) %>%
  mutate(sample_id = 'baseline') %>%
  rbind(empirical.within %>% select(-n, -mean))

ggplot(d.toplot, aes(x = `rep diff`, y = empirical_stat, 
                     fill = sample_id, color = sample_id, group = sample_id)) +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.5, color = NA,
                d.toplot %>% filter(sample_id == 'baseline')) +
    #geom_line(alpha = 0, size = 2) +
    geom_line(size = 1, linetype = 'dashed', data = d.toplot %>% filter(sample_id == 'baseline')) +
    geom_point(size = 2, data = d.toplot %>% filter(sample_id == 'empirical')) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0,
                  data = d.toplot %>% filter(sample_id == 'empirical')) +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F,
                data = d.toplot %>% filter(sample_id == 'empirical')) +
    scale_color_manual(values=c("#d07e93", "#163c4e")) + 
    scale_fill_manual(values=c("#d07e93", "#163c4e")) + 
    scale_x_discrete(labels = c('(1,2)','(2,3)', '(3,4)', '(4,5)', '(5,6)' ,'(6,7)','(7,8)')) +
    ylim(.5, .8) +
    ylab('correlation') +
    ggtitle('within-pair') +
    theme_few() +
    xlab('repetition pair') +
    guides(color = F, fill = F) +
    theme(legend.position = c(0.5, 0.8), text = element_text(size=18), 
          element_line(size=1), element_rect(size=2, color="#00000"))

ggsave('../../../graphical_conventions_latex/cogsci19/figures/source/within.pdf', height = 10, width = 7, units = 'cm', useDingbats = F)
```

## Between-interaction divergence 


```{r}
gamepair.df <- M_mat %>%
  group_by(target, repetition) %>%
  do(flatten_sim_matrix(get_sim_matrix(., F_mat_raw_nonorm, method = 'cor'),
                        .$gameID)) %>%
  unite(col = 'gamepair', dim1, dim2)

true_lmer.across <- lmer(sim ~ poly(repetition, 2) + (1 + repetition | gamepair) + (1 + repetition | target), data = gamepair.df)
true_tstat.across <- coef(summary(true_lmer.across))[,"t value"][2]

permuted_tstats.across <- map_dbl(seq_len(1000), ~ M_mat %>%
 # scrambles repetition
  group_by(target, gameID) %>%
  mutate(repetition = sample(repetition, size = length(repetition))) %>% 
  ungroup() %>%
  arrange(gameID, target, repetition) %>%
  group_by(target,repetition) %>%
  # computes similarity upper triangular
  do(flatten_sim_matrix(get_sim_matrix(., F_mat_raw_nonorm, method = 'cor'), .$gameID)) %>%
  unite(col = 'gamepair', dim1, dim2) %>%
  mutate(sample_id = 1) %>%
  ungroup() %>%
  # turns into a list to make `map` happy
  split(.$sample_id) %>%
  map(~ lmer(sim ~ poly(repetition,2) + (1 + repetition | gamepair) + (1 + repetition | target), data = .)) %>%
  map(~ (tidy(., effects = 'fixed') %>% filter(term == 'poly(repetition, 2)1'))$statistic) %>%
  unlist())

cat('CI=', sort(permuted_tstats.across)[25], sort(permuted_tstats.across)[975])

# ggplot(data.frame(permuted = permuted_tstats.across, true = true_tstat.across),
#        aes(x = 0, y = permuted)) +
#   geom_violin(fill = '#d07e93', alpha = 0.25, color = NA) +
#   geom_point(aes(x = 0, y = true), size = 4, color = "#163c4e") +
#   theme_bw() +
#   ylab('slope t value') +
#   coord_flip() +
#   scale_x_continuous(breaks = NULL) +
#   theme(aspect.ratio = 1/5) 
```

```{r}
empirical.across <- compute_across_similarity(M_mat, F_mat_raw_nonorm,   'raw_cor_nonorm', method = 'cor', nboot = 1000)
baselines.across <- map_dfr(seq_len(1000), ~M_mat %>%
  group_by(target, gameID) %>%
  mutate(repetition = sample(repetition, size = length(repetition))) %>% 
  ungroup() %>%
  compute_across_similarity(F_mat_raw_nonorm, .x, method = 'cor')) 
```

```{r}
d.toplot <- rbind(empirical.across %>% select(-mean, -n),
      baselines.across %>% 
        group_by(repetition) %>%
        summarize(`ci_upper`=quantile(empirical_stat, probs=0.975),
                  `ci_lower`=quantile(empirical_stat, probs=0.025),
                  `empirical_stat`=quantile(empirical_stat, probs=0.5)) %>%
        mutate(sample_id = 'baseline')) %>%
        mutate(repetition = repetition + 1)
ggplot(d.toplot, aes(x = repetition, y = empirical_stat, group = sample_id, 
                     color = sample_id, fill=sample_id)) +
  geom_ribbon(alpha = 0.25, aes(ymin = ci_lower, ymax = ci_upper), color = NA,
              data = d.toplot %>% filter(sample_id == 'baseline')) + 
  geom_line(size = 1, linetype = 'dashed', data = d.toplot %>% filter(sample_id == 'baseline')) +
  geom_point(size = 2, alpha = 1, data = d.toplot %>% filter(sample_id == 'raw_cor_nonorm')) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0,
                 data = d.toplot %>% filter(sample_id == 'raw_cor_nonorm')) +
  geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F,
              data = d.toplot %>% filter(sample_id == 'raw_cor_nonorm')) +
  scale_color_manual(values=c("#d07e93", "#163c4e")) + 
  scale_fill_manual(values=c("#d07e93", "#163c4e")) + 
  xlim(0.5, 8.5) +
  scale_x_continuous(labels = c(1,2,3,4,5,6,7,8), breaks = c(1, 2,3,4,5,6,7,8)) +
  ylim(.5, .8) +
  ylab('correlation') +
  ggtitle('between-pair') +
  theme_few() +
  guides(color = F, fill = F) +
  theme(legend.position = c(0.5, 0.8), text = element_text(size=18), 
        element_line(size=1), element_rect(size=2, color="#00000"))


ggsave('../../../graphical_conventions_latex/cogsci19/figures/source/across.pdf', height = 10, width = 7, units = 'cm', useDingbats = F)
```

## Temporal structure 

```{r}


```

## supplemental

Visualize effects of different pre-processing steps and distance metrics

```{r}
F_mat_raw_norm = as.matrix(read_delim('../../data/sketch_features/no_crop/FEATURES_FC6_sketch_channel-norm.txt',
                                   delim=',', col_names=F))
F_mat_PCA_nonorm = as.matrix(read_delim('../../data/sketch_features/no_crop/FEATURES_FC6_sketch_PCA_512_no-channel-norm.txt',
                                   delim=',', col_names=F))
F_mat_PCA_norm = as.matrix(read_delim('../../data/sketch_features/no_crop/FEATURES_FC6_sketch_PCA_512_channel-norm.txt',
                                   delim=',', col_names=F))

colnames(F_mat_raw_norm) <- NULL
colnames(F_mat_PCA_nonorm) <- NULL
colnames(F_mat_PCA_norm) <- NULL
rbind(compute_across_similarity(filtered_M, F_mat_raw_nonorm, 'raw_euclid_nonorm', method = 'euclidean'),
      compute_across_similarity(filtered_M, F_mat_raw_norm,   'raw_euclid_norm',   method = 'euclidean'),
      compute_across_similarity(filtered_M, F_mat_PCA_nonorm, 'PCA_euclid_nonorm', method = 'euclidean'),
      compute_across_similarity(filtered_M, F_mat_PCA_norm,   'PCA_euclid_norm',   method = 'euclidean'),
      compute_across_similarity(filtered_M, F_mat_raw_nonorm, 'raw_cor_nonorm',    method = 'cor'),
      compute_across_similarity(filtered_M, F_mat_raw_norm,   'raw_cor_norm',      method = 'cor'),
      compute_across_similarity(filtered_M, F_mat_PCA_nonorm, 'PCA_cor_nonorm',    method = 'cor'),
      compute_across_similarity(filtered_M, F_mat_PCA_norm,   'PCA_cor_norm',      method = 'cor')) %>%
      separate(sample_id, into = c('PCA', 'dist', 'norm')) %>%
      ggplot(aes(x = repetition, y = empirical_stat, color = norm)) + 
        #geom_line(alpha = 0.1) +
        geom_line() +
        geom_ribbon(aes(ymax = ci_upper, ymin = ci_lower), color = NA, alpha = .5) +
        theme_few() +
        facet_grid(dist ~ PCA, scales = 'free') +
        theme(aspect.ratio = 2)
  #geom_smooth(group = 1, method = 'loess')
  #geom_smooth(group = 1)
ggsave('unfiltered.pdf')
```

How well are these different steps correlated?

```{r}
rbind(compute_across_similarity(M_mat, F_mat_PCA_norm, 'PCA_cor_norm',    method = 'cor'),
      compute_across_similarity(M_mat, F_mat_raw_nonorm, 'raw_cor_nonorm',    method = 'cor')) %>%
      #separate(sample_id, into = c('PCA', 'dist', 'norm')) %>%
  select(repetition, sample_id, empirical_stat) %>%
  spread(sample_id, empirical_stat) %>%
  mutate(spcor = cor(PCA_cor_norm,raw_cor_nonorm, method='pearson')) %>%
  ggplot(aes(x = PCA_cor_norm, y = raw_cor_nonorm)) +
      geom_point() +
      geom_smooth() +
      theme_few()
```

Broken out by target

```{r}
M_mat %>%
  group_by(target, repetition) %>%
  do(flatten_sim_matrix(get_sim_matrix(., F_mat_raw_nonorm, method = 'cor'),
                        .$gameID)) %>%
  unite(col = 'gamepair', dim1, dim2) %>%
  ggplot(aes(x = repetition, y = sim, group = gamepair)) +
    geom_line(alpha = .1) +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), group = 1) +
    facet_wrap(~ target) +
    theme_few()

ggsave('by_target_gamepair.pdf')
```